---
title: "Raw data Airbnb"
output: pdf_document
date: "2024-03-07"
---

```{r, echo=FALSE}
library(tidyverse)
listings <- read_csv('listings.csv')
calendar <- read_csv('calender.csv')

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

```{r include=FALSE}
library(readr)
library(dplyr)
library(tidyverse)
library(ggplot2)
```


## Analysis of the raw data files

This document shows an analysis of the raw data files for the listings and calendar from airbnb in Barcelona.

```{r}
summary(listings)
summary(calendar)
```

## Listings
The data set 'Listings.csv' contains information for the listings on the site, like the host, location, reviews, etc. 
Below are all of the variables from the dataset:

- 'id': the id number of the listing
- 'name': the title of the listing on the website
- 'host_id': the id number of the host
- 'host_name': the name of the host
- 'neighbourhood_group': the group of neighbourhoods in Barcelona that the room or apartment is located
- 'neighbourhood': the neighbourhood in Barcelona that the room or apartment is located
- 'latitude': the geographic coordinate that refers to the north-south position of the listing
- 'longitude': the geographic coordinate that refers to the east-west position of the listing
- 'roomtype': whether the listing is for an entire home/apartment or a private room
- 'price': the price of the listing
- 'minimum_nights': the minimum amount of nighst you have to rent the room or apartment
- 'number_of_reviews': the numver of reviews left for the listing
- 'last_review': the date of when the last review was posted for the listing
- 'reviews_per_month': the amount of reviews the listing on average gets per month
- 'calculated_host_listings_count': the total number of listings managed by the host
- 'availability_365': the number of days the listing is available to be booked per year
- 'number_of_reviews_ltm': the number of reviews that were written for this listing in the last twelve month


## Calender

- 'listings-id': the id number of the listing
- 'date': the date that the data was retrieved
- 'available': whether the listing is available
- 'price': the price to rent the listing
- 'adjusted_price': 
- 'minimum_nights': the minimum amount of nights you have to rent the room or apartment
- 'maximum_night': the maximum amount of nights you can rent the room or apartment


```{r}




```


You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
