---
title: "The influence of the Primavera Sound festival on Airbnb prices"
output: pdf_document
date: "2024-03-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = FALSE, include=FALSE}
load("model_results.RData")
install.packages("kableExtra", repos = "https://cloud.r-project.org/")
library(kableExtra)
```

## Hypotheses

In this paper we are researching two hypoteses, concerning Airbnb prices during the festival Primavera Sound in Barcelona. The two research questions we are looking into are: 

"Does the presence of a Summer Music Festival influence the prices of Airbnb listings in the respective city?"

"Is it possible to create a model that helps Airbnb hosts to define the pricings of their listings?"

To answer these hypotheses, two datasets for Airbnb listings are used and analyzed. From the data sets, the prices from during and before/after the festival are compared for the listings that are within 5 kilometers of the festival. The research objective is to discover if the prices for the Airbnb listings during the festival are different from normal, and if a model can be created that predicts these price differences. 



## Research method

For the analysis of this research the means for the prices of the listings within 5 kilometers of the festival, are calculated and compared for during the festival and before/after. Moreover, four different linear regression are performed to get a deeper understanding of the differences between these periods. 

```{r, message=FALSE, echo=FALSE}
coefficients <- coef(minimum_nights_during_festival)
std_errors <- summary(minimum_nights_during_festival)$coef[, "Std. Error"]
t_values <- coefficients / std_errors
p_values <- summary(minimum_nights_during_festival)$coef[, "Pr(>|t|)"]

# Create a data frame with the extracted information
regression_summary <- data.frame(
  Coefficients = coefficients,
  `Std. Error` = std_errors,
  `t value` = t_values,
  `Pr(>|t|)` = p_values
)

kable(regression_summary, format = "markdown", digits = 4) %>%
  kable_styling() %>%
  add_header_above(c(" ", "The effect of the minimum amounts of nights on the price of a listing during the festival" = 4))

```


```{r, message=FALSE, echo=FALSE}
coefficients2 <- coef(minimum_nights_off_festival)
std_errors2 <- summary(minimum_nights_off_festival)$coef[, "Std. Error"]
t_values2 <- coefficients2 / std_errors2
p_values2 <- summary(minimum_nights_off_festival)$coef[, "Pr(>|t|)"]

# Create a data frame with the extracted information
regression_summary2 <- data.frame(
  Coefficients = coefficients2,
  `Std. Error` = std_errors2,
  `t value` = t_values2,
  `Pr(>|t|)` = p_values2
)

kable(regression_summary, format = "markdown", digits = 4) %>%
  kable_styling() %>%
  add_header_above(c(" ", "The effect of the minimum amounts of nights on the price of a listing before and after the festival" = 4))

```


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
